Urban Connectivity Dynamics: Analyzing Free Public WiFi Distribution in Toronto

### 2024-04-18 outputs/paper/paper.qmd
add enhancement for appendix

# Appendix 
\newpage

>>>>

# Appendix

For enhancement, I take advantage of shiny, which is to quickly add some interactivity to our graphs according to the simulated data. Here(@fig-shiny) is the screnshot of my shiny work, and the interactive graphis is in the folder "Enhancement - Shiny Plot".

```{r}
#| echo: false
#| warning: false
#| label: fig-shiny
knitr::include_graphics("Shiny.png")
```
